The \dealii Library, Version 9.5

### 2023-06-24 9.5/paper.tex
nonlinear solver

The major changes of this release are:
%
\begin{itemize}
  \item Substantial updates and extensions to \dealii{}'s interfaces
    to other libraries (see Section~\ref{sec:external}). This
    includes, in particular, the integration of \texttt{Kokkos} (Section~\ref{sec:kokkos});
    additions and updates to the \texttt{PETSc} and Trilinos
    interfaces
    (Sections~\ref{sec:petsc} and \ref{sec:trilinos}); and a uniform
    way of defining callbacks used by external libraries
    (Section~\ref{sec:callbacks}).
  \item Advances in matrix-free infrastructure (see Section~\ref{sec:mf});
  \item Advances in non-matching support (see Section~\ref{sec:nonmatching});
  \item New features related to liner algebra (see Section~\ref{sec:lac})
  \item C++ language modernization (see Section~\ref{sec:language}).
\end{itemize}
%

@@

@@

Internally above function uses the new function \texttt{CGALWrappers::compute\_intersection\_of\_cells()}, to actually compute intersections between two geometric entities.

For the common case of Nitsche-type mortaring, quadrature points must be distributed on the intersections to evaluate the underlying physical coupling terms.
The \texttt{intersection\_data} returned by the function above can convert itself to data which can be used to fill \texttt{RemotePointEvaluation}.
The whole procedure is done communication-free.
\begin{c++}
// distribute n_points_1D quadrature points to the intersections
auto point_data = intersection_data.template 
       convert_to_distributed_compute_point_locations_internal<dim>(
         n_points_1D, tria, mapping,
         // following parameter is optional would need additional
         // communication 
         consistent_numbering_of_sender_and_receiver);

@@

Note that the new class \texttt{MGTwoLevelTransferNonNested} is not limited to
multigrid but can be used to prolongate results and restrict residuals between any
two meshes. Indeed, the infrastructure has been successfully applied to perform
conservative interpolation between a fine (near) mesh and a coarse (far) mesh in the
context of aeroacoustic problems.
\todo{Can we add a reference for this?}

>>>>

The major changes of this release are:
%
\begin{itemize}
  \item Substantial updates and extensions to \dealii{}'s interfaces
    to other libraries (see Section~\ref{sec:external}). This
    includes, in particular, the integration of \texttt{Kokkos} (Section~\ref{sec:kokkos});
    additions and updates to the \texttt{PETSc} and Trilinos
    interfaces
    (Sections~\ref{sec:petsc} and \ref{sec:trilinos}).
  \item Uniform handling of nonlinear solver
  packages (Section~\ref{sec:nonlinear}) and a uniform
    way of defining callbacks used by external libraries (Section~\ref{sec:callbacks}).
  \item Advances in matrix-free infrastructure (see Section~\ref{sec:mf}).
  \item Advances in non-matching support (see Section~\ref{sec:nonmatching}).
  \item New features related to linear algebra (see Section~\ref{sec:lac}).
  \item C++ language modernization (see Section~\ref{sec:language}).
\end{itemize}
%

@@

\subsubsection{Uniform interface for nonlinear solvers}\label{sec:nonlinear}

With the current release, \dealii{} now supports solvers for nonlinear problems
provided by several different external packages:
1. KINSOL (part of SUNDIALS), 2. SNES (part of PETSc, see Section~\ref{sec:petsc}), 3. NOX (part of Trilinos, see Section~\ref{sec:trilinos}).
The wrappers are provided by the classes \texttt{PETScWrappers::NonlinearSolver<VectorType>}, \texttt{SUNDIALS::KINSOL<VectorType>}, and \texttt{TrilinosWrappers::NOXSolver<VectorType>}, respectively.

All classes have a very similar interface, except that they vary in the kind of
algorithms and parameters offered. The new class \texttt{NonlinearSolverSelector<VectorType>} provides a wrapper on top of
the three external solvers with a unified interface. The user can either let
\dealii{} decide which of the packages to use (depending on the current availability of
the external packages) or specify it manually.

Here is a complete example of an MPI parallel Newton solver that automatically chooses one of the available packages:
\begin{c++}
    using NLSolver = NonlinearSolverSelector<LA::MPI::Vector>;

    NLSolver::AdditionalData additional_data(NLSolver::automatic,
                                             NLSolver::newton);
    NLSolver nonlinear_solver(additional_data, mpi_communicator);

    nonlinear_solver.reinit_vector = [&](LA::MPI::Vector &x)
                                     {/*...*/};
    nonlinear_solver.residual = [&](const LA::MPI::Vector &evaluation_point,
                                    LA::MPI::Vector &      residual)
                                {/*...*/};
    nonlinear_solver.setup_jacobian = [&](const LA::MPI::Vector &current_u)
                                      {/*...*/};
    nonlinear_solver.solve_with_jacobian = [&](const LA::MPI::Vector &rhs,
                                               LA::MPI::Vector &      dst,
                                               const double tolerance)
                                           {/*...*/};

    nonlinear_solver.solve(current_solution);
\end{c++}

@@

The above function uses the new function \texttt{CGALWrappers::compute\_intersection\_of\_cells()} internally to compute intersections between two geometric entities.

For the common case of Nitsche-type mortaring, quadrature points must be distributed on the intersections to evaluate the underlying physical coupling terms.
The \texttt{intersection\_data} returned by the function above can convert itself to data which can be used to fill \texttt{RemotePointEvaluation}.
The whole procedure is done communication-free.
\begin{c++}
// distribute n_points_1D quadrature points to the intersections
auto point_data = intersection_data.template
       convert_to_distributed_compute_point_locations_internal<dim>(
         n_points_1D, tria, mapping,
         // The following parameter is optional and setting it to 
         // true requires additional communication
         consistent_numbering_of_sender_and_receiver);

@@

Note that the new class \texttt{MGTwoLevelTransferNonNested} is not limited to
multigrid but can be used to prolongate results and restrict residuals between any
two meshes. Indeed, the infrastructure has been successfully applied to perform
conservative interpolation between a fine (near) mesh and a coarse (far) mesh in the
context of aeroacoustic problems.
